---
title: "310657002_林奕勳_hw05-for-mpg-data"
output: html_document
---

Code coming from  https://www.data-to-viz.com/caveat/boxplot.html
```{r}
library('tidyverse')
library(ggplot2)
library(tidyr)
library(dplyr)
library(moments)
library(viridis)
```

```{r}

feature_name_mpg = c('mpg','cylinders','displacement','horsepower','weight','acceleration','model year','origin','car name')
data_mpg = read.table("C:\\Users\\xx958\\OneDrive\\桌面\\nycu 碩一_上\\數據科學\\mpg\\auto-mpg.data",head=F,col.names=feature_name_mpg)
data_mpg = data_mpg[1:8]

str(data_mpg)

# it is show that have 398 datas and 8 variables(mpg is label orthers is feature)
dim(data_mpg)

```

## change type of data to numerice but probuct NA
```{r}
for (i in names(data_mpg)){
  data_mpg[[i]]=as.numeric(data_mpg[[i]])
}
summary(data_mpg)
```

## find NA , and horsepower have 6 NA Missing value
```{r}
colSums(is.na(data_mpg))
data_mpg[is.na(data_mpg$horsepower),]
```

## and remove missing value
```{r}
miss_value = which(is.na(data_mpg$horsepower)==1)
data_mpg = data_mpg[-miss_value,]
```

our label(mpg) have not outlier 
```{r}
boxplot(data_mpg$mpg)
```

plot boxplot anf find that acceleration have outlier 
```{r}
boxplot(data_mpg$acceleration)
```

plot boxplot and find that horsepower have outlier 
```{r}
boxplot(data_mpg$horsepower)
```
find outlier of horsepower
```{r}
quan=quantile(data_mpg$horsepower,c(0.25,0.5,0.75))
IQR_horsepower = quan[3]-quan[1]
outlier_horsepower=which(data_mpg$horsepower > quan[2]+1.5*IQR_horsepower)
data_mpg_outlier_horsepower = data_mpg[outlier_horsepower,]
```

find outlier of acceleration
```{r}
quan=quantile(data_mpg$acceleration,c(0.25,0.5,0.75))
IQR_acceleration = quan[3]-quan[1]
outlier_acceleration=which(data_mpg$acceleration > quan[2]+1.5*IQR_acceleration | data_mpg$acceleration < quan[2]-1.5*IQR_acceleration)
data_mpg_outlier_acceleration = data_mpg[outlier_acceleration,]
```

plot scatter plot of horsepower with mpg , although have outlier but it have small mpg 
```{r}
plot(data_mpg$horsepower,data_mpg$mpg)
points(x=data_mpg_outlier_horsepower$horsepower,y=data_mpg_outlier_horsepower$mpg,col='red')
```
plot scatter plot of acceleration with mpg , although have outlier but when the acceleration small ,the mpg  small , and when acceleration large mpg is irregular 
```{r}
plot(data_mpg$acceleration,data_mpg$mpg)
points(x=data_mpg_outlier_acceleration$acceleration,y=data_mpg_outlier_acceleration$mpg,col='red')
```
plot scatter plot of acceleration and horsepower
```{r}
plot(data_mpg$acceleration,data_mpg$horsepower)
points(x=data_mpg_outlier_acceleration$acceleration,y=data_mpg_outlier_acceleration$horsepower,col='red')
points(x=data_mpg_outlier_horsepower$acceleration,y=data_mpg_outlier_horsepower$horsepower,col='green')
outlier = intersect(outlier_acceleration , outlier_horsepower)
data_mpg_pool_outlier = data_mpg[outlier,]
points(x=data_mpg_pool_outlier$acceleration,y=data_mpg_pool_outlier$horsepower,col='cyan',pch=16)
```

plot boxplot of mpg group by cylinders , and find have outlier 
```{r}
data_mpg%>%
  ggplot(aes(cylinders,mpg ,color =as.factor(data_mpg$cylinders) ))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```

plot boxplot of mpg group by origin, and find have outlier 
```{r}
data_mpg%>%
  ggplot(aes(origin,mpg ,color =as.factor(data_mpg$origin) ))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```

```{r}
data_mpg[['origin']]=as.character(data_mpg[['origin']])
ggplot(data_mpg,aes(x=mpg,group=origin,col=origin,fill=origin))+
  geom_histogram(aes(y=..density..),alpha=0.2,position="identity")+
  geom_density(alpha=0.2)
data_mpg[['origin']]=as.numeric(data_mpg[['origin']])
```

```{r}
data_mpg[['cylinders']]=as.character(data_mpg[['cylinders']])
ggplot(data_mpg,aes(x=mpg,group=cylinders,color=cylinders,fill=cylinders))+
  geom_histogram(aes(y=..density..),alpha=0.2,position="identity")+
  geom_density(alpha=0.2)
data_mpg[['cylinders']]=as.numeric(data_mpg[['cylinders']])
```




find the displacement and weight have high association with mpg
```{r}
panel.cor=function(x,y,digits=2,prefix="",cex.cor=10,...)
  {
  usr=par("usr")
  on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r=cor(x,y)
  txt=format(c(r,0.123456789),digits=digits)[1]
  txt=paste(prefix,txt,sep ="")
  if(missing(cex.cor)) cex.cor=1/strwidth(txt)
  text(0.5,0.5,txt,cex=cex.cor*abs(r))
  } 
pairs(data_mpg,lower.panel=panel.smooth,upper.panel=panel.cor)
```

check distribution for mpg , and find that it is positive skew (i.e skew to right)
```{r}
data_mpg%>%
  ggplot(aes(mpg))+
  geom_histogram(aes(y=..density..),col='black',fill='black',alpha=0.2)+
  geom_density(alpha=0.2,fill='red')
skewness(data_mpg$mpg)
```

and we take log for mpg and find that symmetrical distribution
```{r}
data_mpg['mpg'] = log(data_mpg['mpg'])
data_mpg%>%
  ggplot(aes(mpg))+
  geom_histogram(aes(y=..density..),col='black',fill='black',alpha=0.2)+
  geom_density(alpha=0.2,fill='red')
```
if we take log for mpg , cylinders,displacement ,horsepower and weight will have high association with mpg
```{r}
pairs(data_mpg,lower.panel=panel.smooth,upper.panel=panel.cor)
```

```{r}
data_mpg%>%
  ggplot(aes(cylinders,mpg ,color =as.factor(data_mpg$cylinders) ))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```
compare previous boxplot the outlier are decrease
```{r}
data_mpg%>%
  ggplot(aes(origin,mpg ,color =as.factor(data_mpg$origin) ))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```


compare previous plot
```{r}
data_mpg[['origin']]=as.character(data_mpg[['origin']])
ggplot(data_mpg,aes(x=mpg,group=origin,col=origin,fill=origin))+
  geom_histogram(aes(y=..density..),alpha=0.2,position="identity")+
  geom_density(alpha=0.2)
```

```{r}
data_mpg[['cylinders']]=as.character(data_mpg[['cylinders']])
ggplot(data_mpg,aes(x=mpg,group=cylinders,color=cylinders,fill=cylinders))+
  geom_histogram(aes(y=..density..),alpha=0.2,position="identity")+
  geom_density(alpha=0.2)
```

# Conclusion : 如果 outlier 跟趨勢差不多無需處理，如果跟趨勢有落差可以單獨拿出來探討，以此資料為例 horsepower跟mpg 成反比，若 outlier of horsepower 跟 mpg 成正比或不成反比 可以單獨討論。 












