---
title: "data science hw01 for mpg data"
output: html_document
---
# Homework 2

## read data and confirm data type , we can see that 'horsepower' althought is numerice but type is character , data have 398 observes and 8 variables(mpg is our label so have 7 features)
```{r}
library('tidyverse')
library('ggplot2')
library(boot)
feature_name_mpg = c('mpg','cylinders','displacement','horsepower','weight','acceleration','model year','origin','car name')
data_mpg = read.table("C:\\Users\\xx958\\OneDrive\\桌面\\nycu 碩一_上\\數據科學\\mpg\\auto-mpg.data",head=F,col.names=feature_name_mpg)
data_mpg = data_mpg[1:8]

str(data_mpg)
```
## change type of data to numerice but probuct NA
```{r}
for (i in names(data_mpg)){
  data_mpg[[i]]=as.numeric(data_mpg[[i]])
}
```

## find NA , and horsepower have 6 NA Missing value
```{r}
colSums(is.na(data_mpg))
data_mpg[is.na(data_mpg$horsepower),]
```

## and remove missing value
```{r}
miss_value = which(is.na(data_mpg$horsepower)==1)
data_mpg_remove_miss = data_mpg[-miss_value,]
```

## confirm data 
```{r}
str(data_mpg_remove_miss)
```

## drawing matrix of scatter plot and find displacement ,horsepower and weight have patten with mpg
```{r}
pairs(mpg~., data_mpg_remove_miss)
```

## cylinders and origin is discrete data so drawing box-plots with mpg , and find medians are opposite
```{r}
par(mfrow=c(1,2))
boxplot(mpg  ~ cylinders, data = data_mpg_remove_miss)
boxplot(mpg  ~ origin , data = data_mpg_remove_miss)
```

```{r}

data_mpg_remove_miss[['origin']]=as.character(data_mpg_remove_miss[['origin']])
ggplot(data_mpg_remove_miss,aes(x=mpg,group=origin,color=origin))+
  geom_histogram(binwidth=2,fill="white",position="identity")

data_mpg_remove_miss[['cylinders']]=as.character(data_mpg_remove_miss[['cylinders']])
ggplot(data_mpg_remove_miss,aes(x=mpg,group=cylinders,color=cylinders))+
  geom_histogram(binwidth=2,fill="white",position="identity")
```

# Homework 3

by homework 2

# first method        
we can use average of horsepower to instead missing value on horsepower

and feature horsepower mean is 104.4694 ,Confidence interval is (100.6472,108.2916)  for mean at $\alpha$ =0.05
```{r}
t.test(data_mpg_remove_miss$horsepower,conf.level = 0.95)
```

```{r}
data_mpg_mean = data_mpg
data_mpg_mean[miss_value,]$horsepower=mean(data_mpg_remove_miss$horsepower)
colSums(is.na(data_mpg_mean))
```

```{r}
data_mpg_mean[miss_value,]
```
# second method
we also can use median of horsepower to instead missing value on horsepower          


```{r}
bootMedian <- function(data, indices) median(data[indices])
median_of_horsepower <- boot(data_mpg_remove_miss$horsepower, bootMedian, R = 1000)

mean(median_of_horsepower$t)
sd(median_of_horsepower$t)
```

```{r}
data_mpg_median = data_mpg
data_mpg_median[miss_value,]$horsepower=mean(median_of_horsepower$t)
colSums(is.na(data_mpg_median))
```

```{r}
data_mpg_median[miss_value,]
```

# third method
on plot we can see that horsepower have high Multicollinearity with displacement and weight , so I try fit a linear regression to predict NA , can see that p-value of displacement  and weight is smaller than $\alpha$ =0.05 , so  horsepower have linear association with  displacement and weight
```{r}
horsepower_regression = lm(horsepower~displacement+weight ,data=data_mpg_remove_miss)
horsepower_predict = predict(horsepower_regression,data_mpg[miss_value,][,c(3,5)])
summary(horsepower_regression)
```

```{r}
data_mpg_predict = data_mpg
data_mpg_predict[miss_value,]$horsepower  = horsepower_predict
```

```{r}
data_mpg_predict[miss_value,]
```

