---
title: "310657002_林奕勳_hw04-for-mpg-data"
output: html_document
---

```{r}
library('tidyverse')
library(ggplot2)
library(tidyr)
library(dplyr)
library(moments)
library(viridis)
```

Code coming from  https://www.data-to-viz.com/caveat/boxplot.html
```{r}
library(gghalves)


"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                        position = "dodge", trim = TRUE, scale = "area",
                        show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}

#' @rdname ggplot2-ggproto
#' @format NULL
#' @usage NULL
#' @export
GeomFlatViolin <-
  ggproto("GeomFlatViolin", Geom,
          setup_data = function(data, params) {
            data$width <- data$width %||%
              params$width %||% (resolution(data$x, FALSE) * 0.9)

            # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
            data %>%
              group_by(group) %>%
              mutate(ymin = min(y),
                     ymax = max(y),
                     xmin = x,
                     xmax = x + width / 2)

          },

          draw_group = function(data, panel_scales, coord) {
            # Find the points for the line to go all the way around
            data <- transform(data, xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))

            # Make sure it's sorted properly to draw the outline
            newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                             plyr::arrange(transform(data, x = xmaxv), -y))

            # Close the polygon: set first and last point the same
            # Needed for coord_polar and such
            newdata <- rbind(newdata, newdata[1,])

            ggplot2:::ggname("geom_flat_violin", GeomPolygon$draw_panel(newdata, panel_scales, coord))
          },

          draw_key = draw_key_polygon,

          default_aes = aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                            alpha = NA, linetype = "solid"),

          required_aes = c("x", "y")
)
```

```{r}

feature_name_mpg = c('mpg','cylinders','displacement','horsepower','weight','acceleration','model year','origin','car name')
data_mpg = read.table("C:\\Users\\xx958\\OneDrive\\桌面\\nycu 碩一_上\\數據科學\\mpg\\auto-mpg.data",head=F,col.names=feature_name_mpg)
data_mpg = data_mpg[1:8]

str(data_mpg)

# it is show that have 398 datas and 8 variables(mpg is label orthers is feature)
dim(data_mpg)

```

## change type of data to numerice but probuct NA
```{r}
for (i in names(data_mpg)){
  data_mpg[[i]]=as.numeric(data_mpg[[i]])
}
```

## find NA , and horsepower have 6 NA Missing value
```{r}
colSums(is.na(data_mpg))
data_mpg[is.na(data_mpg$horsepower),]
```

## and remove missing value
```{r}
miss_value = which(is.na(data_mpg$horsepower)==1)
data_mpg = data_mpg[-miss_value,]
```

find the displacement and weight have high association with mpg
```{r}
pairs(data_mpg)
```

check distribution for mpg , and find that it is positive skew (i.e skew to right)
```{r}
data_mpg%>%
  ggplot(aes(mpg))+
  geom_histogram(aes(y=..density..),col='black',fill='black',alpha=0.2)+
  geom_density(alpha=0.2,fill='red')
```
mpg boxplot group by cylinders,and find that cylinders=8 have different others
```{r}
data_mpg%>%
  ggplot(aes(cylinders,mpg ,color =as.factor(data_mpg$cylinders) ))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```
mpg boxplot group by origin,and find that have different weather mediat or average
```{r}
data_mpg%>%
  ggplot(aes(origin,mpg ,color =as.factor(data_mpg$origin) ))+
  geom_boxplot()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```
violin for boxplot
```{r}
data_mpg%>%
  ggplot(aes(origin,mpg ,color =as.factor(data_mpg$origin) ))+
  geom_violin()+
  stat_summary(fun.y=mean, geom="point", shape=5, size= 3)
```
histogram and density for mpg group by origin ,and find skew and distribution are different
```{r}
data_mpg[['origin']]=as.character(data_mpg[['origin']])
ggplot(data_mpg,aes(x=mpg,group=origin,col=origin,fill=origin))+
  geom_histogram(aes(y=..density..),alpha=0.2,position="identity")+
  geom_density(alpha=0.2)
```
kurtosis are different
```{r}
data_mpg[['cylinders']]=as.character(data_mpg[['cylinders']])
ggplot(data_mpg,aes(x=mpg,group=cylinders,color=cylinders,fill=cylinders))+
  geom_histogram(aes(y=..density..),alpha=0.2,position="identity")+
  geom_density(alpha=0.2)
```
from pairs plot find displacement have high association for mpg , thus plot boxplot , histogram and density ,
```{r}
layout(mat = matrix(c(1,2), byrow=TRUE),height = c(1,4))
par(mar=c(0, 3.1, 1.1, 2.1))
boxplot(data_mpg$displacement , horizontal=TRUE , xaxt="n" , col=rgb(0.8,0.8,0,0.5) , frame=F)
points(mean(data_mpg$displacement),1,col='red')
par(mar=c(0, 3.1, 1.1, 2.1))
hist(data_mpg$displacement , breaks=40 ,prob = TRUE, col=rgb(0.2,0.8,0.5,0.5) , border=T,main='')
lines(density(data_mpg$displacement))
```


like previously plot
```{r}
data_mpg%>%
  ggplot(aes(1,displacement,fill='red'))+
  geom_flat_violin()+
  geom_dotplot(binaxis = "y", dotsize = 25, stackdir = "down", binwidth = 0.3, position = position_nudge(-0.025))
```
improve boxplot and we can compare previously boxplot , it is same distribution and consiquence
```{r}
data_mpg%>%
  ggplot(aes(x=origin,y=mpg,group=origin,fill=origin))+
    geom_flat_violin(scale = "count", trim = FALSE, width=2) + 
    geom_dotplot(binaxis = "y", dotsize = 15, stackdir = "down", binwidth = 0.05, position = position_nudge(x=-0.025)) 
```


```{r}

data_mpg%>%
  ggplot(aes(x=as.factor(data_mpg$cylinders),y=mpg,fill=as.factor(data_mpg$cylinders)))+
  geom_flat_violin(scale = "count", trim = FALSE,position = position_nudge(x=.1))+
  geom_dotplot(binaxis = "y", dotsize = 15, stackdir = "down", binwidth = 0.05, position = position_nudge(-0.025))
```






